
---
title: "Module Selection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Module Selection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

DURIAN supports the integration of custom deconvolution modules, even modules written in other languages, such as Julia.  Module selection is made using the `deconv_method` argument to `DURIAN::run_durian` and the default is `deconv_method = "MuSiC"`.

Current deconvolution alternatives include:

-   fast, NNLS regression using [MuSiC (R)](https://github.com/xuranw/MuSiC)
-   distributed Monte Carlo inference using [dsLDA (Julia)](https://github.com/mkarikom/DistributedStwdLDA.jl)

##### Load the package and data
```{r setup,warning=FALSE,message=FALSE}
library(DURIAN)
```

We will run DURIAN with two different deconvolution modules: LDA-based topic model and NNLS-based regression.

We select a random subset of 1000 genes present in both bulk and single-cell data, as well as a subset of 5 patients from the original 20, to speed up the example.

##### Preprocess the data
```{r}
set.seed(42)
B.sub = B[,1:5]
C.sub = as.data.frame(C %>% sample_n(1000))
comgenes = intersect(rownames(C.sub),rownames(B.sub))
C.sub = DURIAN::subsetsc(scremoutlier(C.sub),geneids=comgenes,return_obj=TRUE,nsd=3)
B.sub = B.sub[comgenes,]
pDataC.sub = pDataC[colnames(C.sub),]
```

Run imputation using dsLDA deconvolution (julia).
##### Run imputation on the single-cell data, using the bulk data for supervision.
```{r,warning=FALSE,message=FALSE,results='hide'}
library(JuliaCall)
julia_library("DistributedStwdLDA")
julia_library("Distributed")
julia_call("procsN",as.integer(ncol(B.sub)+1))
julia_command("@everywhere using DistributedStwdLDA")

impresult_list_lda=run_durian(
      scrabble_parameters = c(1,1e-6,1e-4),
      nEM = 5,
      scdata = C.sub,
      metadata = pDataC.sub,
      bulkdata = B.sub,
      deconv_method = "dsLDA",
      MCNITER = as.integer(2000),
      MINCELLSTOPICCORP=as.integer(1),
      MCNPARTITIONS=ncol(B.sub),
      MCNCHAINS=as.integer(1),
      MCTHINNING=as.integer(1),
      MCBURNRATE=0.5,
      LDASCALEBLK="lognorm",
      LDASCALESC="column",
      LDASCALEFACBLK=10000,
      nIter_outer = 10,
      nIter_inner = 10,
      nSDCIters = 500000,
      DECONVGENETHRESH=-0.01,
      SCRGENETHRESH=-0.01,
      outerStats = FALSE,
      durianEps=1e-3,
      saveImputationLog = FALSE,
      saveDeconvolutionLog = FALSE,
      saveImputedStep=FALSE)
  impresult_lda = impresult_list_lda[["C"]]
```

Run imputation using MuSiC deconvolution (R).  Note: by default, the mtSCRABBLE backend for DURIAN imputation (regardless of deconvolution module) calls `irlba::irlba()` for speed when computing matrix norms for the DURIAN objective.  Currently, `irlba` does not gracefully handle the case where a randomly chosen starting singular vector is close to the null space.  When the corresponding error is encountered
##### Run imputation on the single-cell data, using the bulk data for supervision.
```{r,warning=FALSE,message=FALSE,results='hide'}
impresult_list=run_durian(
      scrabble_parameters = c(1,1e-6,1e-4),
      nEM = 1,
      scdata = C.sub,
      metadata = pDataC.sub,
      bulkdata = B.sub,
      deconv_method = "MuSiC",
      nIter_outer = 10,
      nIter_inner = 10,
      nSDCIters = 500000,
      DECONVGENETHRESH=-0.01,
      SCRGENETHRESH=-0.01,
      outerStats = FALSE,
      durianEps=1e-3,
      saveImputationLog = FALSE,
      saveDeconvolutionLog = FALSE,
      saveImputedStep=FALSE)
  impresult = impresult_list[["C"]]
```


##### Construct a low-dimensional UMAP embedding from imputed and original data
```{r,warning=FALSE,message=FALSE,results='hide'}
library(umap)
library(ggplot2)
library(reshape2)
common_cells = base::intersect(base::intersect(colnames(impresult_lda),colnames(impresult)),colnames(C))
umap_imputed_lda = umap(t(impresult_lda[,common_cells]),preserve.seed=TRUE)
umap_imputed = umap(t(impresult[,common_cells]),preserve.seed=TRUE)
umap_orig = umap(t(as.matrix(C[,common_cells])),preserve.seed=TRUE)
imputed_df_lda = cbind(umap_imputed_lda$layout,pDataC.sub[common_cells,])
imputed_df_lda$status = "Imputed [LDA deconv.]"
imputed_df = cbind(umap_imputed$layout,pDataC.sub[common_cells,])
imputed_df$status = "Imputed [W-NNLS deconv.]"
orig_df = cbind(umap_orig$layout,pDataC.sub[common_cells,])
orig_df$status = "Unimputed"
df = rbind(imputed_df,imputed_df_lda,orig_df)
colnames(df) = c("UMAP1","UMAP2","cellID","cellType","sampleID","status")
df$status = factor(df$status,levels=c("Imputed [W-NNLS deconv.]","Imputed [LDA deconv.]", "Unimputed"))
```

##### Plot the original and imputed data
```{r,warning=FALSE,message=FALSE,results='hide', fig.width=7,fig.height=3,dev = "svg",fig.ext="svg"}
ggplot(df,aes(x=UMAP1, y=UMAP2,color=cellType)) + 
      geom_point(size=1)+
      facet_grid(~status,scales="free") + theme_bw()
```
