
---
title: "Imputation/Signaling from Seurat Output"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Imputation/Signaling from Seurat Output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

##### Load the package and data
```{r setup,warning=FALSE,message=FALSE}
library(DURIAN)
data(c("C","B","pDataC"))
```

##### Create Seurat Object
```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
library(Seurat)

### prepare a Seurat object for this example
seur = CreateSeuratObject(counts=C)


seur = NormalizeData(seur)
seur = FindVariableFeatures(seur, selection.method = "vst")
seur = ScaleData(seur)

seur = RunPCA(seur, features = rownames(seur))

seur = RunUMAP(seur, dims = 1:10)
seur = FindNeighbors(seur, dims = 1:5)
seur = FindClusters(object = seur)

seur@meta.data$cellID = rownames(seur@meta.data)
seur@meta.data = dplyr::left_join(seur@meta.data,pDataC,by="cellID")
rownames(seur@meta.data) = seur@meta.data$cellID
```

##### Run imputation on the single-cell data, using the bulk data for supervision.
```{r,warning=FALSE,message=FALSE,results='hide'}
seur=run_durian(
      scrabble_parameters = c(1,1e-6,1e-4),
      nEM = 5,
      seur = seur,
      bulkdata = B,
      deconv_method = "MuSiC",
      nIter_outer = 10,
      nIter_inner = 10,
      nSDCIters = 500000,
      DECONVGENETHRESH=-0.01,
      SCRGENETHRESH=-0.01,
      outerStats = FALSE,
      durianEps=1e-3,
      saveImputationLog = FALSE,
      saveDeconvolutionLog = FALSE,
      saveImputedStep=FALSE)

dim(seur)
```

##### Construct the CellChat Object
Comparing two datasets in CellChat requires unique names for each cell.  Thus, the label of each Seurat assay (`RNA` and `IMPUTED`) is prepended to the cell ID during creation of the individual CellChat objects, prior to merging them.

For full documentation on the CellChat-specific steps below, please refer to [the corresponding CellChat tutorial](https://github.com/sqjin/CellChat/blob/master/tutorial/Comparison_analysis_of_multiple_datasets.html).
```{r,warning=FALSE,message=FALSE,results='hide'}
library(CellChat)

# CellChat Raw Object
CellChatDB = CellChatDB.human
data = normalizeData(as.matrix(GetAssayData(seur,assay="RNA",slot = "counts")))
colnames(data) = paste0("RNA.",colnames(data))
meta = seur@meta.data[,c("cellType","sampleID")]
rownames(meta) = colnames(data)
meta$sampleID = colnames(data)
cellchat <- createCellChat(object = data, meta = meta, group.by = "cellType")
cellchat@DB <- CellChatDB

# Raw Object Processing
cellchat <- subsetData(cellchat)
cellchat <- identifyOverExpressedGenes(cellchat)
cellchat <- identifyOverExpressedInteractions(cellchat)

# Raw Object Individual Probs
cellchat <- computeCommunProb(cellchat,raw.use = TRUE)
cellchat <- computeCommunProbPathway(cellchat)
cellchat <- aggregateNet(cellchat)
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP")

# CellChat Imputed Object
data = normalizeData(as.matrix(GetAssayData(seur,assay="IMPUTED",slot = "counts")))
colnames(data) = paste0("IMPUTED.",colnames(data))
meta = seur@meta.data[,c("cellType","sampleID")]
rownames(meta) = colnames(data)
meta$sampleID = colnames(data)
cellchat_imputed <- createCellChat(object = data, meta = meta, group.by = "cellType")
cellchat_imputed@DB <- CellChatDB

# Imputed Object Processing
cellchat_imputed <- subsetData(cellchat_imputed)
cellchat_imputed <- identifyOverExpressedGenes(cellchat_imputed)
cellchat_imputed <- identifyOverExpressedInteractions(cellchat_imputed)

# Imputed Object Individual Probs
cellchat_imputed <- computeCommunProb(cellchat_imputed,raw.use = TRUE)
cellchat_imputed <- computeCommunProbPathway(cellchat_imputed)
cellchat_imputed <- aggregateNet(cellchat_imputed)
cellchat_imputed <- netAnalysis_computeCentrality(cellchat_imputed, slot.name = "netP")

cellchats_list = list()
cellchats_list[["orig"]] = cellchat
cellchats_list[["imputed"]] = cellchat_imputed
merged = mergeCellChat(cellchats_list, add.names = names(cellchats_list),cell.prefix=TRUE)
```

##### The Impact of Imputation on Number of Interactions Between Cell Types
The impact of imputation is generally data-dependent and asymmetric across pathways.  Changes in the number of interactions between cell types shows that dropout is also cell type specific. 

For full documentation on the CellChat-specific steps below, please refer to [the corresponding CellChat tutorial](https://github.com/sqjin/CellChat/blob/master/tutorial/Comparison_analysis_of_multiple_datasets.html).
```{r}
netVisual_heatmap(merged)
```